### 2022-03-14 02_paper/02_study/paper_methods.Rmd
update paper method section

# create new columns that give proportion of Gender
# percentage = female gender divided by all female Gender
demo.data <- demo.data  %>% 
  group_by(Group) %>% 
  mutate(Gender_percentage = Gender/Gender_Sum) %>% 
  mutate(Gender_percentage = round(sum(Gender_percentage)*100, digits=0))

# create a basic table (tibble) using tidyverse functions
demo.table <- demo.data %>%
  group_by(Group) %>%
  summarise(N=n(),
            "Gender female in percentage" = Gender_percentage,
            "M Age in years" = round(mean(Age), 0),
            "SD Age in years" = round(sd(Age), 0),
            "Min Age in years" = min(Age),
            "Max Age in years" = max(Age),
            "M Exp. in years" = round(mean(`Teaching Experience`), 0),
            "SD Exp. in years" = round(sd(`Teaching Experience`), 0),
            "Min Exp. in years" = min(`Teaching Experience`),
            "Max Exp.in years" = max(`Teaching Experience`),
           )

@@

The expert teachers (`r sum(demo.data$Gender)`women, `r demo.data$Gender_percentage`%) had a mean age of

>>>>

# create new columns that give proportion of Gender
# percentage = female gender divided by all female Gender
# demo.data <- demo.data  %>% 
#   group_by(Group) %>% 
#   mutate(Gender_percentage = Gender/Gender_Sum) %>% 
#   mutate(Gender_percentage = round(sum(Gender_percentage)*100, digits=0))

# create a basic table (tibble) using tidyverse functions
demo.table <- demo.data %>%
  group_by(Group) %>%
  summarise(N=n(),
            "Gender female in percentage" = round(sum(Gender/Gender_Sum) * 100, digits = 0),
            "M Age in years" = round(mean(Age), 2),
            "SD Age in years" = round(sd(Age), 2),
            "Min Age in years" = min(Age),
            "Max Age in years" = max(Age),
            "M Exp. in years" = round(mean(`Teaching Experience`), 2),
            "SD Exp. in years" = round(sd(`Teaching Experience`), 2),
            "Min Exp. in years" = min(`Teaching Experience`),
            "Max Exp.in years" = max(`Teaching Experience`),
           )

@@

The expert teachers (`r demo.data %>% filter(Gender == 1 & Group == "Expert") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Expert") %>% pull("Gender female in percentage")`%) had a mean age of `r demo.data %>% filter(Group == "Expert") %>% pull(Age) %>% mean() %>% round(., digits = 2)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Age in years") %>% round(., digits = 2)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Age in years")`) with average teaching experience of `r demo.data %>% filter(Group == "Expert") %>% pull("M Exp. in years") %>% mean() %>% round(., digits = 2)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Exp. in years") %>% round(., digits = 2)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Exp. in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Exp. in years")`).

The novice teachers (`r demo.data %>% filter(Gender == 1 & Group == "Novice") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Novice") %>% pull("Gender female in percentage")`%) had a mean age of `r demo.data %>% filter(Group == "Novice") %>% pull(Age) %>% mean() %>% round(., digits = 2)` years (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Age in years") %>% round(., digits = 2)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Age in years")`).
